Different forms of uncertainty differently affect the evolution of social learning

### 2022-08-11 ms.tex
updated all sensitivity analyses with N=1000
Updates from Overleaf

\textbf{Selection set size.}
When one does not know which option to take, uncertainty increases with the number of options, which we call the selection set size.
% This is a mathematical fact at the
% core of information theory: the number of bits required to reliably encode the optimal solution increases by one every time the
% selection set doubles in size~\cite{mackay2003information}. 
% This is intuitive; the more options to consider, the greater one's uncertainty about which option is the best choice. 
In studies of social learning, the selection set is often limited
to just two options.  For example, in empirical studies of \emph{bombus
terresteris} (bumble bee)~\cite{Baracchi2018} and \emph{parus major} (great
tit)~\cite{Aplin2017}, experimenters provided two behaviors for the bees or birds
to choose from, where one yielded a higher payoff than the other. %respectively,
each yielding greater or smaller payoffs depending on experimental treatment.
Similarly, many human studies have used just two or three possible
behaviors~\cite{McElreath2005,Toyokawa2019}. Behavioral study designs are
often motivated by modeling studies with similar formulations~\cite{Rogers1988,boyd1995does,
perreault2012bayesian}.
% \cm{pretty sure boyd1995 uses same trick as
% rogers 88 so not sure why they were being used as illustrating separate kinds of
% behavior selection sets. correct if wrong} 
Larger, more open sets of behavioral
choices are not uncommon in experiments trying to capture more complex or
naturalistic tasks~\cite{derex2013, wasielewski2014}, but these map on
imperfectly to the theoretical literature \mt{How so?}. Some models have studied systems with
larger, but defined, selection sets~\cite{Rendell2010}, while in others the
number of options is implicit in the model payoff structure
~\cite{Enquist2007} \mt{How does this work exactly in Enquist et al 2007?}. 
Researchers have also compared models with a different number
of environment states, corresponding to a different number of optimal behaviors
through time ~\cite{Feldman1996}. These examples share one common feature: 
the size of the selection set was held static \emph{within} model generations.
% as a measure of changing uncertainty in cultural evolutionary models.

>>>>

\textbf{Selection set size.}
When one does not know which option to take, uncertainty increases with the number of options, which we call the selection set size.
% This is a mathematical fact at the
% core of information theory: the number of bits required to reliably encode the optimal solution increases by one every time the
% selection set doubles in size~\cite{mackay2003information}. 
% This is intuitive; the more options to consider, the greater one's uncertainty about which option is the best choice. 
In studies of social learning, the selection set is often limited
to just two options.  For example, in empirical studies of \emph{bombus
terresteris} (bumble bee)~\cite{Baracchi2018} and \emph{parus major} (great
tit)~\cite{Aplin2017}, experimenters provided two behaviors for the bees or birds
to choose from, where one yielded a higher payoff than the other. %respectively,
each yielding greater or smaller payoffs depending on experimental treatment.
Similarly, many human studies have used just two or three possible
behaviors~\cite{McElreath2005,Toyokawa2019}. Behavioral study designs are
often motivated by modeling studies with similar formulations~\cite{Rogers1988,boyd1995does,
perreault2012bayesian}.
% \cm{pretty sure boyd1995 uses same trick as
% rogers 88 so not sure why they were being used as illustrating separate kinds of
% behavior selection sets. correct if wrong} 
Larger, more open sets of behavioral
choices are not uncommon in experiments trying to capture more complex or
naturalistic tasks~\cite{derex2013, wasielewski2014}, but these map on
imperfectly to the theoretical literature that tend to use a limited set of behavioral options.
%\mt{How so?}. 
Some models have studied systems with
larger, but defined, selection sets~\cite{Rendell2010}, while in others the
number of options is implicit in the probability that a learner gets the right answer.
~\cite{Enquist2007} 
%\mt{How does this work exactly in Enquist et al 2007?}. 
Researchers have also compared models with a different number
of environment states, corresponding to a different number of optimal behaviors
through time ~\cite{Feldman1996}. These examples share one common feature: 
the size of the selection set was held static \emph{within} model generations.
% as a measure of changing uncertainty in cultural evolutionary models.
